%====================
% EXPERIENCE A
%====================
\subsection{{Software Engineer \hfill October 2018 --- Present}}
\subtext{Practio \hfill Lisbon, Portugal}

\begin{itemize}
    \item Full stack development of a platform used in the Healthcare industry,
	to help healthcare staff, such as, pharmacists 
	and doctors to register information about patients and 
	help them perform severals types of consultations, 
	such as, travel vaccinations.
    \begin{itemize}
        \item Backend: NodeJS, ExpressJS, MongoDB
        \item Frontend: Javascript (ES6), React, Redux, Stylus
    \end{itemize}
\end{itemize}

%====================
% EXPERIENCE B
%====================
\subsection{{Android Developer \hfill June 2017 - October 2018}}
\subtext{Tekever \hfill Lisbon, Portugal}
\begin{zitemize}
\item Native Android apps for some of the biggest Portuguese 
electrical power providers. 
The main goal was to help workers perform their job of 
installing new equipment and getting the values 
from smart meters.
\begin{itemize}
    \item Android apps: Java, Android Studio
\end{itemize}
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{Software Developer \hfill November 2015 - June 2017}}
\subtext{Novabase \hfill Lisbon, Portugal}
\begin{zitemize}
\item Android, iOS and web applications for several clients.
\begin{itemize}
    \item Android Apps: Java, Android Studio
    \item iOS Apps: ObjectiveC, XCode
    \item Web applications:
    \begin{itemize}
        \item Backend: Java, OracleDB
	    \item Frontend: Javascript, CSS, HTML
    \end{itemize}
\end{itemize}
\end{zitemize}

%====================
% EXPERIENCE D
%====================
\subsection{{Software Developer \hfill October 2013 - October 2015}}
\subtext{FenixEdu \hfill Lisbon, Portugal}
\begin{zitemize}
\item Organization inside college that was in charge of developing 
the academic information system, 
used there and in other institutions, to manage everything
related to the students, staff, etc. 
Other projects were also being developed here. 
As a developer here (at the same time I was graduating) 
I worked in python libraries and several web applications.
\begin{itemize}
    \item Python libraries. The main goal of these libraries was to provide
    SDKs for other apps to use the Fenix API features, such as, get
    students data, enroll student in exams and much more: Python, Django
    \item Web applications. Includes the academic information system
    and other side projects inside the organization.
    \begin{itemize}
        \item Backend: Backend: Java, Jersey, Python, Django, FenixFramework (ORM developed inhouse)
        \item Frontend: Javascript, HTML, Javascript, Angular, React
    \end{itemize}
\end{itemize}
\end{zitemize}

%====================
% EXPERIENCE D
%====================
\subsection{{Software Developer \hfill July 2013 - September 2013}}
\subtext{Table \& Friends \hfill Lisbon, Portugal}
\begin{itemize}
\item Web application to book tables at restaurants
\begin{itemize}
    \item Integration between the existent web app with a Javascript library, 
    in order to get analytics data and send it to Google Analytics and Mixpanel: 
    Javascript, JQuery
    \item Native Android app: Java, Android Studio
\end{itemize}
\end{itemize}
